The ChEMBL database as Linked Open Data

### 2012-04-11 article.tex
Added an intro for the application section

>>>>

The ChEMBL-RDF is increasingly used, and we here present a few applications. The first application
describes how it uses the SPARQL end point can be used to make the data available as linked data
via the Bio2RDF platform. The second application takes advantage of the bibliographic information
exposed as machine readable data, in calculating citation statistics. The third application shows
an integration of ChEMBL-RDF with ChemSpider to provide an extension for the decision support
platform in Bioclipse. The last application shows how Chem2Bio2RDF can combine the ChEMBL data
with other life sciences databases, showing the power of the Linked Data approach.
